---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rparquet

<!-- badges: start -->
<!-- badges: end -->

The goal of rparquet is to provide a nanoarrow-based Parquet file reader with minimal install footprint. It's currently an experiment and barely works at all (see Example).

## Installation

You can install the development version of rparquet from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/rparquet")
```

Installation requires a rust compiler.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rparquet)

schema <- nanoarrow::nanoarrow_allocate_schema()

rparquet:::parquet_read_schema(
  "inst/extdata/penguins.parquet",
  nanoarrow::nanoarrow_pointer_addr_chr(schema)
)

schema
```
